Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-23 DGMM2025/paper.tex
rearrangement + adding missing data
added pictures to show visibility

    \section{Feature-aware normal estimation on digital surfaces}

@@

                    390235 10000000\\ % TODO récup le temps demain (en ~10e4s)

@@

>>>>

    % Insert visibility results images

    \begin{figure}
        \begin{center}
            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
            \caption{Visibility of a point on an edge of a fandisk}
            \label{fig:visibility-fandisk}
        \end{center}
    \end{figure}
    \begin{figure}
        \begin{center}
            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
            \label{fig:visibility-torus-knot}
        \end{center}
    \end{figure}

    % Quantitative results

@@

                    390235 10493200\\

@@

    \section{Feature-aware normal estimation and curvature estimation on digital surfaces}

    % Explain how i use the resulting visibility to compute the normals

    % Then same with curvatures

    % Graphical result comparison of curvatures
